Case study of Scalable Quantum Simulation of Molecular Energies

### 2019-06-21 article.tex
miki U quote

\section{Conclusion and outlook}
As this is the first scalable simulation of molecular energies on any type of quantum hardware it represents an important step in the history of
quantum computing applications. The results indicate that for near-term quantum devices without effective error correction the adaptive approach
represented by the Variational Quantum Eigensolver may have better error resilience than that of standard gate model approach represented by the
Phase Estimation Algorithm. The expectation is that this work will pave the way for the development of further techniques for intractable calculations
 in quantum chemistry. And the final aim is that eventually these variational quantum chemistry techniques will allow for numerically exact simulations
  of chemical reaction rates, which are of great industrial commercial value. In particular, the efficiency - requiring only short state preparation
   and measurement procedures, and so it is without the normal substantial overhead required for quantum error correction - and robustness to
   error displayed by the experimental implementation of the variational quantum eigensolver technique indicates that this technique might succeed
    where classical techniques fail in solving traditionally intractable problems.

>>>>

\section{Conclusion and outlook}

As this is the first scalable simulation of molecular energies on any type of quantum hardware it represents an important step in the history of
quantum computing applications. The results indicate that for near-term quantum devices without effective error correction the adaptive approach
represented by the Variational Quantum Eigensolver may have better error resilience than that of standard gate model approach represented by the
Phase Estimation Algorithm. The expectation is that this work will pave the way for the development of further techniques for intractable calculations
 in quantum chemistry. And the final aim is that eventually these variational quantum chemistry techniques will allow for numerically exact simulations
  of chemical reaction rates, which are of great industrial commercial value. In particular, the efficiency - requiring only short state preparation
 and measurement procedures, and so it is without the normal substantial overhead required for quantum error correction - and robustness to
 error displayed by the experimental implementation of the variational quantum eigensolver technique indicates that this technique might succeed
 where classical techniques fail in solving traditionally intractable problems.

 Mikolaj Uryszek, a researcher in the Strongly Correlated Electron Systems group at UCL, commented that "variational techniques in quantum chemistry
 are becoming increasingly prevalent as a useful benchmarking tool for Noisy Intermediate-Scale Quantum devices, and this paper by O’Malley et al.
 represents one of the most accurate quantum chemistry simulations to date, and is a certainly a promising validation of the development of
 superconducting qubits for scalable quantum hardware".
